\documentclass[a4paper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor} % Added for graying out text

\titleformat{\section}{\large\bfseries}{}{0em}{}
\renewcommand{\thesection}{}

\begin{document}

\begin{center}
    {\LARGE \textbf{Kelebogile Ruben Thabane}} \\
    \href{https://www.linkedin.com/in/kelebogile-thabane-566863187}{linkedin.com/in/kelebogile-thabane-566863187}
 \item \textbf{Junior Support IT Technician} 
\end{center}
\space

\section{About Me}
I am a seasoned professional in technology and business enablement from South Africa. Currently pursuing NQF 6 IT Cloud Solutions Engineering, I specialize in streamlining processes and ensuring compliance. With expertise in full-stack development using JavaScript, Angular.js, and Jenkins, I have a track record of delivering efficient solutions. Previous roles include technical support at PC IT Solutions, focusing on hardware maintenance and customer satisfaction. Fluent in English and Setswana, I am passionate about leveraging technology to drive business success and make a positive impact.

\section{Personal Details}
\begin{itemize}
    \item \textbf{Gender:} Male
    \item \textbf{Nationality:} South African
    \item \textbf{Languages:} English, Setswana
    \item \textbf{Date of Birth:} 25 June 2000
    \item \textbf{Location:} Johannesburg, South Africa
\end{itemize}

\section{Contact Information}
\begin{itemize}
    \item \textbf{Phone:} 081 478 5580 / 064 765 5738
    \item \textbf{Email:} \href{mailto:Kele.ply@gmail.com}{Kele.ply@gmail.com}
    \item \textbf{Website:} \href{https://kelebogile-thabane.netlify.app}{kelebogile-thabane.netlify.app}
%   \item \textbf{GitHub:} \href{https://github.com/Kelebogil}{github.com/Kelebogil}
\end{itemize}

\section{Education}
\begin{itemize}
    \item \textbf{CTU Training Solutions} – 2024 \newline
    NQF 6 - IT Cloud Solutions Engineer
    \item \textbf{The Digital Academy (Speccon)} – 2022 \newline
    NQF 5 - IT System Support
    \item \textbf{Kgatelopele Secondary School} – 2018 \newline
    National Senior Certificate
\end{itemize}

\section{Work Experience}

\textbf{Yellotec} (March 2025- Present)\\
\textcolor{gray}{Junior IT Support Technician}
\begin{itemize}
    \item Assisting end users with hardware and software issues including desktops, laptops, and peripherals.
    \item Responded to help desk tickets and provided support via telephone, email, and in person.
    \item Set up and configured new equipment and software applications.
    \item Maintaing SQL databases for all clients and ensuring Data is being backed up on the SQL Database
\end{itemize}


\textbf{SANBS} (July 2024 - Nov 2024)\\
\textcolor{gray}{Junior IT Support Technician (Intern)}
\begin{itemize}
    \item Assisted end users with hardware and software issues including desktops, laptops, and peripherals.
    \item Responded to help desk tickets and provided support via telephone, email, and in person.
    \item Set up and configured new equipment and software applications.
    \item Ensured smooth IT operations and user satisfaction while learning daily.
\end{itemize}

\textbf{ABSA RBB} (July 2023 - November 2023)\\
\textcolor{gray}{Junior Specialist Business Enablement}
\begin{itemize}
    \item Provided specialist advice and support in managing and delivering business initiatives.
    \item Reviewed and evaluated documentation for new customer accounts to ensure compliance.
\end{itemize}

\textbf{The Digital Academy} (November 2021 - November 2022)\\
\textcolor{gray}{Full Stack Developer (Intern)}
\begin{itemize}
    \item Developed and maintained responsive and visually appealing front-end web applications using HTML, CSS, and JavaScript frameworks.
\end{itemize}

\textbf{ABSA RBB} (June 2022 - November 2022)\\
\textcolor{gray}{Junior Full Stack Developer (Intern)}
\begin{itemize}
    \item Built and maintained applications using C\# and React.js, Angular.js.
    \item Worked with Jenkins for testing and deploying applications.
    \item Conducted meetings with clients to translate business requirements into technical solutions.
\end{itemize}

\textbf{PC IT Solutions} (January 2021 - September 2021)\\
\textcolor{gray}{Technical Support Technician}
\begin{itemize}
    \item Assembled and disassembled desktops and laptops.
    \item Maintained and updated computer hardware and software according to user preferences.
\end{itemize}


\section{Skills}
\begin{minipage}{0.5\textwidth}
\begin{itemize}
    \item Googling
    \item Interpersonal Skills
    \item Problem-solving
    \item Communication
\end{itemize}
\end{minipage}%
\begin{minipage}{0.5\textwidth}
\begin{itemize}
    \item Web Development
    \item Debugging
    \item Troubleshooting
\end{itemize}
\end{minipage}

\section{References}
\textbf{The Digital Academy}\\
Mr. Sithembiso Mhlanga – IT Technician\\
\textbf{Phone:} 060 976 2027\\
\textbf{Email:} Sithembiso.Mhlanga@sanbs.org.za\\

Mr. Tommas Fihla – Team Leader\\
\textbf{Phone:} 067 280 6288\\
\textbf{Email:} tomas@thedigitalacademy.co.za\\

\textbf{Absa RBB}\\
Tracy Lebitso Sesenyi – Business Enablement Manager\\
\textbf{Phone:} 063 681 3569\\

Sandile Moyo – Business Enablement Manager\\
\textbf{Phone:} 082 609 2668

\end{document}
